Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-04 krs-survey.tex
Light edition of the scenario section

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{figs/brownie_scenario.jpg}
	\caption{A representation of the scenario, in the MORSE simulator}
	\label{fig|scenario}
\end{figure*}

@@

A ``first-order'' analysis of this task leads to a first partition of the
required representation abilities:

@@

We mentioned that a recipe often provides a procedure (or a \emph{plan}). The robot
should be able to store this plan in a way that allow later execution.  The
plan is likely to contain \emph{spatio-temporal constraints} (like ``put
the brownie in the oven for 20 min'') that must as well be appropriately
represented.

To make decision, a robot may also want to \emph{predict} the state of the world
after some action (``if I leave the cake 2h in the oven, it will be burned'').
Such ability to project itself in future or, generally speaking, in other
possible state of the world is related to several cognitive ability and
reasoning techniques: \emph{planning}, \emph{representation of possible worlds}
and \emph{non-monotonic reasoning}, in addition to common-sense knowledge and
\emph{physics-based reasoning}.

Procedures are in addition often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened to put the cake in the oven.
Such underspecification should be detectable, representable, and ideally
completable by the knowledge representation system\footnote{Note that we do not
assume here the {\it knowledge representation system} to be a single software
component: it may well be the result of the aggregation of several modules
working together}.

@@

Cooperation in our scenario can intervene at many places. For instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. This \emph{helping} behaviour makes sense only if
the first agent knows that the recipient agent both needs the information but
does not know it. This in turn requires the robot to be able to model the
knowledge of the other agents: to think \emph{from the perspective} of another
agent (this idea is related to the so-called Theory of Mind~\cite{...}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general~\cite{Jakobson} requires the addresser and the
addressee to share a common interpretative framework (shared common-sense
knowledge -- or cultural background -- and a shared context). In our scenario,
the agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Besides the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this so-called \emph{grounding}
operation is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding usually denotes the {\it top-down}
operation: from the symbol to the percept. It is however commonly bundled with
the converse operation, that retrieve (or create) symbols from perception.

@@

In order to effectively share tasks, the robot must also know what it is
capable of: \emph{capability introspection} (both in term of general capability
and of immediate ability) is thus often desirable. More general introspection
(like the ability to tell ``who I am'' or ``what do I think of'' does not
appear to be necessary in our scenario. This may however enrich the human-robot
interaction.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{figs/brownie_scenario.jpg}
	\caption{A possible representation of the scenario, in the MORSE simulator}
	\label{fig|scenario}
\end{figure*}

@@

A ``first-order'' analysis of this task leads to a rough partition of the
required representation abilities:

@@

We mentioned that a recipe often provides a procedure (or a \emph{plan}). The
robot should be able to store this plan in a way that allow later execution.
The plan is likely to contain \emph{spatio-temporal constraints} (like ``put
the brownie in the oven for 20 min'' or ``let's cook \emph{for tonight}'') that
must as well be appropriately represented.

To make decision, a robot may also want to \emph{predict} the state of the world
after some action (``if I leave the cake 2h in the oven, it will burn'').
Such ability to project itself in future or, generally speaking, in other
possible state of the world is related to several cognitive ability and
reasoning techniques: \emph{planning}, \emph{representation of possible worlds}
and \emph{non-monotonic reasoning}, in addition to common-sense knowledge and
\emph{physics-based} reasoning (that allows to predict that an egg is likely to
break if dropped).

Procedures are in addition often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened to put the cake in the oven.
Such underspecification should be detectable, representable, and ideally
completable by the knowledge representation system\footnote{Note that we do not
assume here the {\it knowledge representation system} to be a single software
component: it may well be the result of the aggregation of several logical
components working together}.

@@

Cooperation in our scenario can intervene at many places. For instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. This \emph{helping} behaviour makes sense only if
the first agent knows that the recipient agent both needs the information but
does not know it. This in turn requires the robot to be able to model the
knowledge of the other agents: to think \emph{from the perspective} of another
agent (this idea is related to the so-called Theory of Mind~\cite{Leslie2000}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general~\cite{Jakobson1960} requires the addresser and the
addressee to share a common interpretative framework (a shared common-sense
knowledge -- or cultural background -- and a shared context). In our scenario,
the agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Behind the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this so-called \emph{grounding}
operation is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding usually denotes the {\it top-down}
operation: from the symbol to the percept. It is however commonly bundled with
the converse operation, that retrieve (or create) symbols from perception.

@@

In order to effectively share tasks, the robot must also know what it is
capable of: \emph{capability introspection} (both in term of general capability
and of immediate ability) is thus often desirable. More general introspection
(like the ability to tell ``who I am'' or ``what do I think of'' does not
appear to be necessary in our scenario. This may however be required in more
general human-robot interaction.
